---
title: "Homework_2"
author: "Khyathi Balusu(kb42582)"
date: "2/4/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Question 1

Max is in a pie-eating contest that lasts 1 hour. Each torte that he eats takes 2 minutes. Each apple pie that he eats takes 3 minutes. He receives 4 points for each torte and 5 points for each pie. What should Max eat to get the most points? Solve the problem using the graphical method.  
Next, let’s see what happens if he would like to stick to his preference of eating at least as many pies as tortes. That is; the number of pies he eats should be greater than or equal to the number of tortes. By how many points does this constraint decrease Max’s total points?

***

$x$ = torte count
$y$ = apple pie count  

max of  $4*x+5*y$
constraint: $2*x+3*y \le 60$.  

We can use graphical method:

###

```{r}
x <- c(0:30)
y <- -2/3*x + 20
plot(x, y, type="l", xlim = c(-5,40), ylim=c(-5,30), axes = FALSE, 
     xlab = "torte count", ylab = "apple pie count")
axis(1, pos=0); axis(2, pos=0)
polygon(x = c(0,0,30), y = c(0,20,0), col = "black")
abline(a=0, b=-4/5, col = "blue")
text(x=0, y = -2, labels = "4x+5y=0", col = "red",pos=4)
points(x=0, y=0, col="blue", pch=19)
abline(a=20, b=-4/5, col = 'blue')
text(x=0, y = 20, labels = "4x+5y=100", col = "red",pos=4)
points(x=0, y=20, col="blue", pch=19)
abline(a=24, b=-4/5, col = "blue")
text(x=30, y = 2, labels = "4x+5y=120", col = "red",pos=4)
points(x=30, y=0, col="blue", pch=19)
text(x=30, y = -2, labels = "(30,0)")
```

upon consuming 30 torte, Max gets 120 points 

Additional constraint:that number of pies is at least as many as torte($y \ge x$), 

Change in graph:


```{r}
x <- c(0:30)
y <- -2/3*x + 20
plot(x, y, type="l", xlim = c(-5,40), ylim=c(-5,30), axes = FALSE, 
     xlab = "torte count", ylab = "apple pie count")
axis(1, pos=0); axis(2, pos=0)
polygon(x = c(0,0,12), y = c(0,20,12), col = "black")
abline(a=0, b =1, col ="red")
abline(a=0, b=-4/5, col = "blue")
points(x=0, y=0, col="blue", pch=19)
text(x=0, y = -2, labels = "4x+5y=0", col = "red",pos=4)
abline(a=20, b=-4/5, col = 'blue')
points(x=0, y=20, col="blue", pch=19)
text(x=0, y=20, labels = "4x+5y=100", col = "red",pos=4)
abline(a=21.6, b=-4/5, col = "blue")
points(x=12, y=12, col="blue", pch=19)
text(x=13, y = 12, labels = "4x+5y=108", col = "red",pos=4)
text(x=12, y = 10, labels = "(12,12)")
```

MAx gets 108 points -  12 points decrease because of additional constraint


## Question 2

A farmer in Iowa owns 450 acres of land. He is going to plant each acre with wheat or corn. Each acre planted with wheat (corn) yields \$2,000(\$3,000) profit, requires three (two) workers, and requires two (four) tons of fertilizer. There are currently 1,000 workers and 1,200 tons of fertilizer available.  

  a) Formulate the optimization problem and solve the problem graphically.
  b) Solve the problem in R and verify that the solutions are the same.
  c) What happens to the decision variables and the total profit when the availability of fertilizer varies from 200 tons to 2200 tons in 100-ton increments? When does the farmer discontinue producing wheat? When does he stop producing corn? (Run a loop for different values of availability of fertilizer from 200 tons to 2200 tons).



a. 
Let x = wheat arc size and 
y = corn arc size. 
Constraints:
* $x + y \le 450$
* $3x + 2y \le 1000$
* $2x + 4y \le 1200$

Graph:

###

```{r}
x <- c(0:500)
y <- -3/2*x + 500
plot(x, y, type="l", xlim = c(-5,500), ylim=c(-5,500), axes = FALSE, 
     xlab = "wheat size", ylab = "Corn size")
axis(1, pos=0); axis(2, pos=0)
polygon(x = c(0,0,200,1000/3), y = c(0,300,200,0), col="black")
abline(a=450, b =-1)
abline(a=300, b=-1/2)
abline(a=0, b=-2/3, col="blue")
points(x=0, y=0, col="blue", pch=19)
text(x=0, y = 20, labels = "2000x+3000y=0", col = "red",pos=4)
abline(a=300, b=-2/3, col="blue")
points(x=0, y=300, col="blue", pch=19)
text(x=0, y = 320, labels = "2000x+3000y=900000", col = "red",pos=4)
abline(a=1000/3, b=-2/3, col="blue")
points(x=200, y=200, col="blue", pch=19)
text(x=200, y = 220, labels = "2000x+3000y=1000000", col = "red",pos=4)
text(x=200, y = 170, labels ="(200, 200)")
```

Solution: 
1. 200 acres with wheat 
2. 200 acres with corn 
3. \$1,000,000 profit

###

b. R solution

###

```{r warning=FALSE}
library("lpSolve")
objective.in <- c(2000, 3000)
const.mat <- matrix(c(1,1,
                      3,2,
                      2,4), nrow = 3, ncol = 2, byrow = TRUE)
const.rhs <- c(450, 1000, 1200)
const.dir <- c("<=", "<=", "<=")
optimum <- lp(direction = "max", objective.in, const.mat, const.dir, const.rhs)
optimum$solution
optimum$objval
```

Solution: 
1. 200 acres with wheat 
2. 200 acres with corn 
3. \$1,000,000 profit

###

c. Dynamic fertilizer:

###
```{r}
df_raw <- data.frame()
df_int <- data.frame()
for(i in c(seq(200, 2200, 100))){
  objective.in <- c(2000, 3000)
  const.mat <- matrix(c(1,1,
                        3,2,
                        2,4), nrow = 3, ncol = 2, byrow = TRUE)
  const.rhs <- c(450, 1000, i)
  const.dir <- c("<=", "<=", "<=")
  
  optimum <- lp(direction = "max", objective.in, const.mat, const.dir, const.rhs)
  df_raw <- rbind(df_raw, data.frame(Fertilizer = i, Wheat=optimum$solution[1],
                  Corn = optimum$solution[2], Profit=optimum$objval))
  
  optimum_int <- lp(direction = "max", objective.in, const.mat, const.dir, const.rhs,
                    all.int = TRUE)
  df_int <- rbind(df_int, data.frame(Fertilizer = i, Wheat=optimum_int$solution[1], 
                  Corn = optimum_int$solution[2], Profit=optimum_int$objval))
  
}
df_raw    # Result without integer condition
df_int    # Result with integer condition
```

### 
Solution: 
without integer condition

1. Fertilizer +> 1800 - Discontinue wheat
2. Wheat = 600 - Discontinue corn



## Question 3

Star Oil Company is considering five different investment opportunities. Table 1 below gives the cash outflows and net present values in millions of dollars. Star Oil has \$40 million available for investment now (time 0); it estimates that one year from now (time 1) \$20 million will be available for investment. Star Oil may purchase any fraction of each investment. In this case, the cash outflows and NPV are adjusted accordingly.  

For example, if Star Oil purchases one-fifth of investment 3, then a cash outflow of 1/5 × 5 = \$1 million would be required at time 0, and a cash outflow of 1/5 × 5 = $1 million would be required at time 1. The one-fifth share of investment 3 would yield an NPV of 1/5 × 16 = \$3.2 million. Star Oil wants to maximize the NPV that can be obtained by investing in investments 1-5. Formulate an LP that will help achieve this
goal. Assume that any funds leftover at time 0 cannot be used at time 1.


Investment | 1  | 2  | 3  | 4 | 5 
--- | --- | --- |--- |--- |---
Time 0 Cash Outflow | 11 | 53 | 5 | 5 | 29
Time 1 Cash Outflow | 3 | 6 | 1| 34
NPV | 13 | 16 | 16 | 14 | 39

***

Function :
* $13x_{1}+16x_{2}+16x_{3}+14x_{4}+39x_{5}$

Constraint:  
* $11x_{1}+53x_{2}+5x_{3}+5x_{4}+29x_{5} \le 40$  
* $3x_{1}+6x_{2}+5x_{3}+x_{4}+34x_{5} \le 20$

###

```{r}
objective.in <- c(13, 16, 16, 14, 39)
const.mat <- matrix(c(11, 53, 5, 5, 29,
                      3, 6, 5, 1, 34), nrow = 2, ncol = 5, byrow = TRUE)
const.rhs <- c(40, 20)
const.dir <- c("<=", "<=")
optimum <- lp(direction = "max", objective.in, const.mat, const.dir, const.rhs)
optimum$solution
optimum$objval
```



## Question 4

The goal of the diet problem is to select a set of foods that will satisfy a set of daily nutritional requirement at minimum cost. Suppose there are three foods available, corn, milk, and bread. Besides, there are restrictions on the number of calories (between 2000 and 2250) and the amount of Vitamin A (between 5000 and 50,000). The table below shows, for each food, the cost per serving, the amount of Vitamin A per serving, and the number of calories per serving. Also, suppose that the maximum number of servings for each food is 10.


Food | Cost Per Serving | Vitamin | Calories 
--- | --- | --- |---
Corn | \$0.18 | 107 | 72 
2% Milk | \$0.23 | 500 | 121
Wheat Bread | \$0.05 | 0 | 65

***

Variables  
* $x_{1}$ : Corn  
* $x_{2}$ : Milk  
* $x_{3}$ : Bread  

Function: 
* Minimize $0.18x_{1}+0.23x_{2}+0.05x_{3}  

Constraint:  
* $72x_{1}+121x_{2}+65x_{3} \ge 2000$
* $72x_{1}+121x_{2}+65x_{3} \le 2250$
* $107x_{1}+500x_{2} \ge 5000$
* $107x_{1}+500x_{2} \le 50000$
* $x_{1} \le 10$
* $x_{2} \le 10$
* $x_{3} \le 10$  
* $x_{1}, x_{2}, x_{3}$ 

###


```{r}
objective.in <- c(0.18, 0.23, 0.05)
const.mat <- matrix(c(72, 121, 65,
                      72, 121, 65,
                      107, 500, 0,
                      107, 500, 0,
                      1, 0, 0,
                      0, 1, 0,
                      0, 0, 1), nrow = 7, ncol = 3, byrow = TRUE)
const.rhs <- c(2000, 2250, 5000, 50000, 10, 10, 10)
const.dir <- c(">=", "<=", ">=", "<=", "<=", "<=", "<=")
optimum <- lp(direction = "min", objective.in, const.mat, const.dir, 
              const.rhs, all.int = TRUE) # with integer condition
optimum$solution
optimum$objval
```

###

Solution:
1. 2 corns
2. 10 milk
3. 10 wheat bread





## Question 5

Paper and wood products companies need to define cutting schedules that will maximize the total wood yield of their forests over some planning period. Suppose that a firm with control of 2 forest units wants to identify the best cutting schedule over a planning horizon of 3 years. Forest unit 1 has a total acreage of 2 and unit 2 has a total of 3. The studies that the company has undertaken predict that each acre in unit 1(2) will have 1, 1.3, 1.4 (1, 1.2, 1.6) tons of woods available for harvesting in year 1, 2, 3 respectively. Based on its prediction of economic conditions, the company believes that it should harvest at least 1.2, 1.5, 2 tons of wood in year 1, 2, 3 separately. Due to the availability of equipment and personnel, the company can harvest at most 2, 2, 3 tons of wood in year 1, 2, 3. What is this company’s best cutting strategy that maximizes the total weights of wood? Here discounting of the time value should not be considered.


***


Variabless:  
* $x_{i}$ : unit 1 in year for wood $i$  
* $y_{i}$ : unit 2 in year for wood $i$  

Constraints:   
* $x_{1}+y_{1} \ge 1.2$  
* $x_{2}+y_{2} \ge 1.5$  
* $x_{3}+y_{3} \ge 2$  
* $x_{1}+y_{1} \le 2$  
* $x_{2}+y_{2} \le 2$  
* $x_{3}+y_{3} \le 3$  
* $x_{2} \le (2-x_{1})*1.3$  
* $x_{3} \le [(2-x_{1})\*1.3-x_{2}]*1.4/1.3$  
* $y_{2} \le (3-y_{1})*1.2$  
* $y_{3} \le [(3-y_{1})\*1.2-y_{2}]*1.6/1.2$  
###
```{r}
objective.in <- c(1,1,1,1,1,1)
const.mat <- matrix(c(1,0,0,1,0,0,
                      0,1,0,0,1,0,
                      0,0,1,0,0,1,
                      1,0,0,1,0,0,
                      0,1,0,0,1,0,
                      0,0,1,0,0,1,
                      1.3,1,0,0,0,0,
                      1.4,1.4/1.3,1,0,0,0,
                      0,0,0,1.2,1,0,
                      0,0,0,1.6,4/3,1), nrow=10, ncol=6, byrow = TRUE)
const.rhs <- c(1.2,1.5,2,2,2,3,2.6,2.8,3.6,4.8)
const.dir <- c(">=",">=",">=","<=","<=","<=","<=","<=","<=","<=")
optimum <- lp(direction = "max", objective.in, const.mat, const.dir, 
              const.rhs)
optimum$solution
optimum$objval
```
As a result, the amounts of wood for harvesting in unit1 are 0.4615385, 2, 0 tons in year 1, 2, 3. And the amounts of wood for harvesting in unit2 are 1.125, 0, 6.586538 tons in year 1, 2, 3.
Solution:
1. unit 1 - 0.4615385, 2, 0 tons for 1, 2, 3 years cons.
2. unit 2 - 1.125, 0, 6.586538 tons for 1, 2, 3 years cons.

