---
title: "HW7"
author: "Khyathi Balusu"
date: "4/27/2020"
output: pdf_document
---

# Question 1


The Bellman equation is:

$$V(i,t) = min(c_{i,j} + V(j,t+1)$$

where i = node number at time t
      t = columns in the picture (we have 4 columns)
      c = cost of that path
      V(i,t) = the shortest path from node i at column t to the node 10
      

## t = 4

$$V(10,4) = 0 $$
## t = 3

$$ V(6,3) = c_{6,10}+V(10,4) = 3$$
$$ V(7,3) = c_{7,10}+V(10,4) = 4$$

$$ V(8,3) = c_{8,10}+V(10,4) = 2$$
$$ V(9,3) = c_{9,10}+V(10,4) = 3$$

## t = 2

$$ V(3,2) = min(c_{3,6}+V(6,3), c_{3,7}+V(7,3))  = min(6, 6) = 6$$
$$ V(4,2) = min(c_{4,6}+V(6,3), c_{4,8}+V(8,3, c_{4,9}+V(9,3))  = min(7, 4, 8) = 4$$
$$ V(5,2) = min(c_{5,7}+V(7,3), c_{5,8}+V(8,3))  = min(6, 4) = 4$$

## t = 1

$$ V(1,1) = min(c_{1,3}+V(3,2), c_{1,4}+V(4,2))  = min(9, 6) = 6$$
$$ V(2,1) = min(c_{2,3}+V(3,2), c_{2,4}+V(4,2), c_{2,5}+V(5,2))  = min(10, 6, 8) = 6$$

Shortest path from:

Node 1 = 1 - 4 - 8 - 10
Node 2 = 2- 4 -8- 10.

Shortest distance for both the paths are 6


# Question 2


The Bellman equation is:

$$V(s,t) = min( c_{s} + V(s+1,t+1), p - rv_{s} + c_{1}+V(1,t+1))$$
where c(s) = operating cost of a car( used for s years)
      p = price of  car
      rv(s) = resale value of a car (used for s years)
      V(s,t) = lowest cost at year t for a car (used for s years)


```{r}
rm(list = ls())

NP = 20000
RV = c(14000,12000,8000,6000,4000,2000)
c = c(600,1000,1600,2400,3200,4400)
T = 6

V = matrix(NA,nrow = T, ncol = T) 
## columns- year
##rows - number of years for which the car has been used

tvalues = seq(1,6)
svalues = seq(1:6)

rownames(V) = svalues
colnames(V) = tvalues

names(c) = svalues
names(RV) = svalues

U =V

t = tvalues[T]

V[,paste(t)] = -RV

for (j in rev(tvalues[1:T-1])){
  for (i in svalues[1:j]){
    v_no_r = V[paste(i+1),paste(j+1)] + c[paste(i+1)]
    v_r = V[paste(1),paste(j+1)]+ NP - RV[paste(i)] + c[paste(1)]
    V[paste(i),paste(j)] = min(c(v_no_r,v_r))
    U[paste(i),paste(j)] = which.min(c(v_no_r,v_r))
  }
}

print(U)

```

### We should keep  the car for the first 2 years, replace and keep again for 2 years ( year 4) and sell it off at the end of year 6. The total cost would be 8800(not considering the intial investment of 20000)


# Question 3


The Bellman equation is:

$$V(i,t) = max_{j = 1,2,3}( V(j,t+1)+ E_{i} - TC_{i,j})$$
where e = earnings
      c = travelling cost from i to j
      V(i,t) = value when he is at place i( on day t)
      j = 1 Indianapolis 
      2 = Blomington
      3 = Chicago



## t = 4

He is required at IndianaPolis, hence negative(infinity) is assigned V(2,4) and V(3,4) 

## t= 3

$$ V(1,3) = max_{j = 1,2,3}(V(j,4)+E_{1} - TC_{1,j}) = 120 $$
$$ V(2,3) = max_{j = 1,2,3}(V(j,4)+E_{2} - TC_{2,j}) = 160-50 = 110 $$
$$ V(3,3) = max_{j = 1,2,3}(V(j,4)+E_{3} - TC_{3,j}) = 170-20 = 150 $$
## t = 2

$$ V(1,2) = max_{j = 1,2,3}(V(j,3)+E_{1} - TC_{1,j}) = max(120+120, 120 - 50 + 110 , 120 - 20 + 150) = 250 $$
$$ V(2,2) = max_{j = 1,2,3}(V(j,3)++E_{2} - TC_{2,j}) = max(160 - 50 + 120, 160 + 110 , 160 - 70 + 150) = 270 $$
$$ V(3,2) = max_{j = 1,2,3}(V(j,3)+E_{3} - TC_{3,j}) = max(170 - 20 + 120, 170 -70 + 110 , 170  + 150) = 320 $$

## t = 1

$$ V(1,1) = max_{j = 1,2,3}(V(j,2)+E_{1} - TC_{1,j}) = max(120+250, 120 - 50 + 270 , 120 - 20 + 320) = 420 $$
$$ V(2,1) = max_{j = 1,2,3}(V(j,2)+E_{2} - TC_{2,j}) = max(160 - 50 + 250, 160+ 270 , 160 - 70 + 320) = 430 $$
$$ V(3,1) = max_{j = 1,2,3}(V(j,2)+E_{3} - TC_{3,j}) = max(170 - 20 +250, 170 - 70 + 270 , 170 + 320) = 490 $$


If he is at Bloomington, we have, 

$$ V(2,0) = max_{j = 1,2,3}(V(j,1)+TC_{2,j} + ) = max(370,430,420) = 430 $$

### It is not precisely Bellman's equation.

### Closest optimum solution will be to be at Bloomington, stay there for the first 3 days and then go to Indianapolis



# Question 4

## states

$$ state variable = [s,t]$$
where t = year 
      s = time used by machine in years at time t
      

## Bellman equation is:

Condition 1:  s+1 < n

$$ v(s,t) = max(-c + p(0)+ v(1,t+1), p(s)+v(s+1,t+1))$$

Condition 2:

$$ v(s,t) = -c + p(0)+ v(1,t+1)$$


# Question 5
SuperMarket chain purchases 6 gallons of milk - sells at three stores
HEB purchase rate - $1
HEB selling rate - $2
Unused milk - 50cents

Cost price - $1
Selling price - $2
unused- 50 cents


The Bellman equation is:

$$ V(x,s) = max_{x in (0 to 6)} (min(x, d(s))*1 - max (0, x-d(s))*0.5 + V(6 -x, s+1))$$ 
where V(x,s) - x gallons of milk sent to store s
      d(s)  - demand at store s
      



```{r}

rm(list = ls())

dem = c(1.8,1.9,1.9) ## expected demand-value

profGains = rep(0,6)
opt = rep(0,3)
optProfit = rep(0,3)

for (s in 1:3){
  for (x in 0:6){

      v = (min(x,dem[s])*1) - (max(0,x-dem[s])*0.5)
      profGains[x] = v
      opt[s] = which.max(profGains)
      optProfit[s] = max(profGains)
}
}

sum(optProfit)
```


Optimal solution - alloting 2 gallons of milk at each store @ profit of $5.4