---
title: "SCO Project 1 - Group 20"
author: "Aadithya Anandaraj, Anisha Alluru, Khyathi Balusu"
date: "2/9/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("Project1.RData")
```


# Q1

# Part 1
The decision variables are the amounts invested in each campaign.

The objective at hand is to maximize the ROI of the investment which is given by
$$(0.031*Print) + (0.049*TV) + (0.024*SEO) + (0.039*AdWords) + (0.016*Facebook) + (0.024*LinkedIn) + (0.046*Instagram) + (0.026*Snapchat) + (0.033*Twitter) + (0.044*Email)$$
The constraints are as follows:
a.
$$Print + TV <= Facebook + Email$$
$$Print + TV - Facebook - Email<= 0$$

b.
$$Facebook + LinkedIn + Instagram + Snapchat + Twitter >= 2*(SEO + AdWords)$$
$$Facebook + LinkedIn + Instagram + Snapchat + Twitter - 2*SEO - 2*AdWords >= 0$$

c.
$$Print <= 3, TV<=3, SEO<=3 ..... Email<=3$$

d. Budget Constraint
$$Print + TV + SEO + .... + Twitter + Email <=10$$
e.
$$Print,TV,SEO, .... ,Twitter,Email >=0 $$

```{r}
library(lpSolve)
c=rep(c(0.031, 0.049, 0.024, 0.039, 0.016, 0.024, 0.046, 0.026, 0.033, 0.044))
A=matrix(0,13,10)
A[1,1:10]=c(1,1,0,0,-1,0,0,0,0,-1)
A[2,1:10]=c(0,0,-2,-2,1,1,1,1,1,0)
A[3:12,1:10]=diag(10)
A[13,1:10]=rep(1,10)
A
dir=c("<=",'>=','<=',rep('<=',10))
B=c(0,0,rep(3,10),10)
```

# Part 2
```{r}
alc1=lp("max",c,A,dir,B)
alc1$solution
alc1$objval
```

# Part 3
```{r}
library(base)
#setwd('D:/ANISHA/DOCUMENTS/Studies/MSBA/Course Work/Spring 2019/Stochastic Control and Optimization/Group Projects/Project 1')
source('allocation_g20.R')
result = allocation(c(0.031, 0.049, 0.024, 0.039, 0.016, 0.024, 0.046, 0.026, 0.033, 0.044), 3, 10)
result$objval
result$solution
```

# Part 4
```{r}
library(base)
#setwd('D:/ANISHA/DOCUMENTS/Studies/MSBA/Course Work/Spring 2019/Stochastic Control and Optimization/Group Projects/Project 1')
#source(allocation_g20.R)
alc2 = allocation(c(0.031, 0.049, 0.024, 0.039, 0.016, 0.024, 0.046, 0.026, 0.033, 0.044), 10, 10)
cat('Without upper bound constraint:\n')
alc2$objval
alc2$solution

cat('With upper bound constraint:\n')
alc1$objval
alc1$solution

cat('The difference in both objective values is ', alc2$objval-alc1$objval)
```
# Q2

#Part 1

Using the new ROI vector,

```{r}
library(base)
#setwd('D:/ANISHA/DOCUMENTS/Studies/MSBA/Course Work/Spring 2019/Stochastic Control and Optimization/Group Projects/Project 1')
#source(allocation_g20.R)
alc3 = allocation(c(0.049, 0.023, 0.024, 0.039, 0.044, 0.046, 0.026, 0.019, 0.037, 0.026), 3, 10)
cat('With upper bound constraint and new ROI:\n')
alc3$objval
alc3$solution
```
The objective value is the same as their counterparts using the previous ROI vector, but the allocation is different.

#Part 2

```{r}
library(base)
#setwd('D:/ANISHA/DOCUMENTS/Studies/MSBA/Course Work/Spring 2019/Stochastic Control and Optimization/Group Projects/Project 1')
#source(allocation_g20.R)
alc1_new_obj=((0.023*3)+(0.039*1)+(0.026*3)+(0.026*3))
alc2_new_obj=((0.023*5)+(0.026*5))
disappointment_alc1 = alc1$objval - alc1_new_obj
disappointment_alc2 = alc2$objval - alc2_new_obj

cat('Disappointment alc1')
disappointment_alc1
cat('Disappointment alc2')
disappointment_alc2
```

The 3rd constraint is valuable as relaxing the upper bound has a higher disappointment.

#Part 3
```{r}
library(base)
#setwd('D:/ANISHA/DOCUMENTS/Studies/MSBA/Course Work/Spring 2019/Stochastic Control and Optimization/Group Projects/Project 1')
#source(allocation_g20.R)

alc1_avg=(alc1$objval+alc1_new_obj)/2
alc2_avg=(alc2$objval+alc2_new_obj)/2

alc3_old_obj=((0.031*3)+(0.039*1)+(0.016*3)+(0.024*3))
alc3_avg=(alc3_old_obj+alc3$objval)/2

#tweaking the ROI vector
old_ROI=c(0.031, 0.049, 0.024, 0.039, 0.016, 0.024, 0.046, 0.026, 0.033, 0.044)
new_ROI=c(0.049, 0.023, 0.024, 0.039, 0.044, 0.046, 0.026, 0.019, 0.037, 0.026)
avg_ROI=(old_ROI+new_ROI)/2
avg_ROI

alc=allocation(c(avg_ROI), 4, 10)
cat('The solution is')
alc$solution
cat('Objective value')
alc$objval
cat('Average objective value of alc1')
alc1_avg
cat('Average objective value of alc2')
alc2_avg
cat('Average objective value of alc3')
alc3_avg
```
By tweaking the ROI vector to be the average of the old and the new ROI vector and changing the upper bound to 4, we obtained the allocation above that dominates the average objective values of the previous (alc1,alc2,alc3). 


# Q3

# Part1

```{r}
monthBudget = 10

A<-matrix(0,13,10)
A[1,]<-c(1,1,0,0,-1,0,0,0,0,-1)
A[2,]<-c(0,0,2,2,-1,-1,-1,-1,-1,0)
A[3,]<-c(rep(1,10))
A[4:13,]<-diag(10)

dir<-c(rep("<=",13))


outputMatrix = matrix(0,12,10)

for (i in 1:12){
  #objective coefficients
  monthROI<-c(ROI_mat[i,]/100)
  
  b<-c(0,0,monthBudget,rep(3,10))
  
  monthAllocation=lp("max",monthROI,A,dir,b,compute.sens = 1)
  
  
  monthSolution=monthAllocation$solution
  monthObjective=monthAllocation$objval
  
  outputMatrix[i,] = monthSolution
  monthBudget = monthBudget + 0.5*monthObjective
}

print (outputMatrix)


```

# Part2

Multi period allocation is the iteration run over monthly budget of the previous month. This would make the first year's investment same irrespective of multi period or previous problem's single problem allocation.

# Part 3

With the newly added constraints, this solution would not hold good. If the monthly change should be no more than 1M, for a stable relationship with each platform given, then with the constrains, the first year solutions would wary.



