---
title: "HW5_kb42582"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=TRUE}
hotel = read.csv("HHonors_booking.csv", header=T)
str(hotel)
hotel$customerID = as.factor(hotel$customerID)


interval = c( )
for(i in 1:400) {
   hotel.i = hotel[hotel$customerID==i,]
   interval.i = rep(0, 50)
   sinceBooking = 0
   for(t in 1:50) {
       sinceBooking = sinceBooking + 1
       interval.i[t] = sinceBooking
       if (hotel.i$Booking[t] == 1) sinceBooking = 0
   }
   interval = c(interval, interval.i)
}
hotel$Interval = interval       
head(hotel)
```

#Q2 - Logistic Model creation

2). Estimate the following logistic regression model using the R function glm( ) 

log(λi(t)/(1- λi(t)) = 0 + 1×Intervalit + 2×Priceit +3×Promotionit 
                                  + 4×Incomei +5×Genderi 
                                                   
And paste results here. How do you interpret 1, 2, 3, 4, 5? Are they statistically significant? Please calculate the AIC and BIC of this model.

Next, we will estimate the model:

log(λi(t)/(1- λi(t)) = 0 + 1×Intervalit + 2×Intervalit2 + 3×Priceit +4×Promotionit 
                                  + 5×Incomei +6×Genderi 

Use poly(Interval, 2) in the glm() function to represent 1×Intervalit+2×Intervalit2 in  this model. Are 1, , 6 still statistically significant? Please calculate the AIC and BIC of this model.



```{r, include=TRUE}

# Logistic Regression with linear coefficients for Interval
hotel.logit1 = glm(Booking~Interval+Price+Promotion+Income+Gender, data=hotel, family=binomial(link="logit"))
print("The Summary of Logit")
summary(hotel.logit1)

hotel.logit2 = glm(Booking~poly(Interval,2)+Price+Promotion+Income+Gender, data=hotel, family=binomial(link="logit"))
print("The Summary of Logit with Square of Interval")
summary(hotel.logit2)

AIC(hotel.logit1)
AIC(hotel.logit2)
BIC(hotel.logit1)
BIC(hotel.logit2)

```


3). Estimate the following cloglog regression model using the R function glm( ) 

log(-log(1- λi(t)) = 0 + 1×Intervalit + 2×Priceit +3×Promotionit 
                                  + 4×Incomei +5×Genderi 
                                                   
Paste results here. Are they statistically significant? How do you interpret 1, 2, 3, 4, 5? Please calculate the AIC and BIC of this model.

```{r, include=TRUE}
hotel.cloglog1=glm(Booking~Interval+Price+Promotion+Income+Gender, data=hotel, family=binomial(link="cloglog"))
print("The Summary of C-loglog Model")
summary(hotel.cloglog1)

AIC(hotel.cloglog1)
BIC(hotel.cloglog1)
```

4) Next, we will let the intercept be a random effect 0i in both the logistic and cloglog models

log(λi(t)/(1- λi(t)) = 0i + 1×Intervalit + 2×Priceit +3×Promotionit 
                                  + 4×Incomei +5×Genderi 
log(-log(1- λi(t)) = 0i + 1×Intervalit + 2×Priceit +3×Promotionit 
                                  + 4×Incomei +5×Genderi 

Using the R function glmer() with link="logit"  and link="cloglog" to estimate these two model and paste results here. Please also calculate the AIC and BIC of these two models.
                                                               
Based on the AIC's and BIC's of the five models in (2), (3) and (4), which is the best model for the data? 
```{r, include=TRUE}

library(lme4)
hotel.logit_re=glmer(Booking~Interval+Price+Promotion+Income+Gender+(1|customerID), data=hotel, family=binomial(link="logit"))
print("The Summary of logit RE Model")
summary(hotel.logit_re)

AIC(hotel.logit_re)
BIC(hotel.logit_re)


library(lme4)
hotel.cloglog_re=glmer(Booking~Interval+Price+Promotion+Income+Gender+(1|customerID), data=hotel, family=binomial(link="cloglog"))
print("The Summary of cloglog RE Model")
summary(hotel.cloglog_re)

AIC(hotel.cloglog_re)
BIC(hotel.cloglog_re)


```









```

## R Markdown

