---
title: "Marketing Homework 3"
author: "Khyathi Balusu - kb42482"
date: "3/2/2020"
output: word_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Binary Data Regression Models for Bank Customer Attrition 

# Q1

```{r}
bankRetentionData = read.csv('Bank_Retention_Data.csv')
```

```{r}
bankRetentionData$TractID = as.factor(bankRetentionData$TractID)
```

Logistic Regression
```{r}
churnlogit <- glm(bankRetentionData$Churn ~ bankRetentionData$Age + bankRetentionData$Income + bankRetentionData$HomeVal + bankRetentionData$Tenure + bankRetentionData$DirectDeposit + bankRetentionData$Loan + bankRetentionData$Dist + bankRetentionData$MktShare, data = bankRetentionData, family = binomial(link = "logit"))
summary(churnlogit)
```

Probit Regression
```{r}
churnprobit <- glm(bankRetentionData$Churn ~ bankRetentionData$Age + bankRetentionData$Income + bankRetentionData$HomeVal + bankRetentionData$Tenure + bankRetentionData$DirectDeposit + bankRetentionData$Loan + bankRetentionData$Dist + bankRetentionData$MktShare, data = bankRetentionData, family = binomial(link = "probit"))
summary(churnprobit)
```

<INSERT BETA INTERPRETATIONS>

```{r}
cat("AIC : ")
AIC(churnlogit)
AIC(churnprobit)
cat("BIC : ")
BIC(churnlogit)
BIC(churnprobit)
```

Probit is slightly better as it's AIC, BIC values are lower.

# Q2
```{r}
library(lme4)
churnrandom <- glmer(Churn ~ (1|TractID) + Age + Income + HomeVal + Tenure + DirectDeposit + Loan + Dist + MktShare, data = bankRetentionData, family=binomial)
summary(churnrandom)
```

```{r}
cat("AIC : ")
AIC(churnrandom)
cat("BIC : ")
BIC(churnrandom)
```
From the summary table, we see that 
Age
Income
HomeVal 
Tenure
DirectDeposit
Dist 
are still statistically significant.

 
# Q3
```{r}
library(MCMCpack)
churnmcmchlogit = MCMChlogit(bankRetentionData$Churn ~ bankRetentionData$Age + bankRetentionData$Income + bankRetentionData$HomeVal + bankRetentionData$Tenure + bankRetentionData$DirectDeposit + bankRetentionData$Loan + bankRetentionData$Dist + bankRetentionData$MktShare, data = bankRetentionData, group = 'TractID', random=~1, r=2, R=1, burnin=10000, mcmc=20000, thin=20)
```

```{r}
summary(churnmcmchlogit$mcmc[,1:9])
```

From the summary table, we see that 
Age, 
Income, 
HomeVal, 
Tenure, 
DirectDeposit, 
Loan, 
Dist  
MarketShare 
are statistically significant at the 5% level


```{r}
plot(churnmcmchlogit$mcmc[,3])
```
```{r}
plot(churnmcmchlogit$mcmc[,6])
```

# Count Data Analysis for Shopping Mall Visits

# Q4
```{r}
mallVisitData = read.csv('Mall_visit.csv')
```

```{r}
mallVisitData$customerID = as.factor(mallVisitData$customerID)
```

```{r}
visit.poisson = glm(Visit ~ Discount + Target + Income + Distant + Gender, data=mallVisitData, family = poisson(link = "log"))
summary(visit.poisson)
```
From the summary table, we see that 
Discount, 
Distant, 
Income, 
Gender 
are statistically significant.


```{r}
cat("AIC : ")
AIC(visit.poisson)
cat("BIC : ")
BIC(visit.poisson)
```

# Q5
```{r}
library(lme4)
visit.poisson.random = glmer(Visit ~ (1|customerID) + Discount + Target + Income + Distant + Gender, data = mallVisitData, family = poisson)
```

```{r}
summary(visit.poisson.random)
```

From the summary table, we see that 
Discount, 
Distant, 
Income 
are statistically significant. 
Gender is no more significant
1, 3, 4   are statistically significant because their p-values are less than 0.05

```{r}
cat("AIC : ")
AIC(visit.poisson.random)
cat("BIC : ")
BIC(visit.poisson.random)
```

# Q6
```{r}
library(MASS)
visit.nb <- glm.nb(Visit ~ Discount + Target +  Income + Distant + Gender, data=mallVisitData)
summary(visit.nb)
```

From the summary table, we see that 
Discount, 
Distant, 
Income, 
Gender are statistically significant. 


```{r}
cat("AIC : ")
AIC(visit.nb)
cat("BIC : ")
BIC(visit.nb)
```
Best model is random effects model with lowest AIC of 44695

# Q7
```{r}
library(MCMCpack)
mallVisitData.mcmc <- MCMChpoisson(fixed=Visit ~ Discount + Target + Distant + Income + Gender, data=mallVisitData, random=~1, group="customerID", burnin=10000, mcmc=20000, thin=20, r=1, R=diag(1))
summary(mallVisitData.mcmc$mcmc[,1:6])
```

Without Random effects: 
Discount, 
Distant, 
Income  
Gender 
are significant. Target is insignificant.

With Random effects: 
Discount, 
Target, 
Distant, 
Income  
Gender are significant.


```{r}
plot(mallVisitData.mcmc$mcmc[,3])
```

